Analysis paper

### 2021-05-24 analysis/analysis.Rmd
add distribution plot for wis

```{r}
scores <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "location_name", "forecast_date", 
                   "location_target", "classification"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[model != "Baseline"]

@@

```{r}
scores[, target_type := paste0(str_to_title(target_type), "s overall")]
p_combined <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ target_type, ncol = 1) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))

p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ location_target) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50)) + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank())
```

```{r}
# scores for different phases of the epidemic
scores[, target_phase := str_to_title(paste0(target_type, "s - ", 
                                             classification, " phase"))]
scores[, target_phase := factor(target_phase, 
                                levels = str_to_title(c("Cases - decreasing phase", 
                                                        "Cases - unclear phase", 
                                                        "Cases - increasing phase", 
                                                        "Deaths - decreasing phase", 
                                                        "Deaths - unclear phase", 
                                                        "Deaths - increasing phase")))]

@@

p_phases <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ target_phase) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

@@

>>>>

```{r}
scores <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "location_name", "forecast_date", 
                   "target_phase",
                   "location_target", "classification"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

@@

```{r}
scores[, target_type := paste0(str_to_title(target_type), "s overall")]

# look at variance to check
scores[, .(sd = sd(scaled_rel_skill)), by = c("model")]

distribution_plot <- function(df, x = "scaled_rel_skill") {
  df %>%
  ggplot(aes_string(y = "model", x = x, 
                          group = "model", fill = "model")) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
}

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
  ggplot(aes_string(y = "model", x = x, 
                          group = "model", fill = "model")) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 1))
}

p_combined <- distribution_plot(df = scores[model != "Baseline"]) + 
  facet_wrap(~ target_type, ncol = 1)

p_combined_wis <- distribution_plot_wis(df = scores, 
                                        x = "interval_score") +
  facet_wrap(~ target_type, ncol = 1, scales = "free_x")

p <- distribution_plot(df = scores[model != "Baseline"]) + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2)

p_wis <- distribution_plot_wis(df = scores) + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2, scale = "free_x")

```{r}
# scores for different phases of the epidemic
scores[, target_phase := factor(target_phase, 
                                levels = str_to_title(c("Cases - decreasing phase", 
                                                        "Cases - unclear phase", 
                                                        "Cases - increasing phase", 
                                                        "Deaths - decreasing phase", 
                                                        "Deaths - unclear phase", 
                                                        "Deaths - increasing phase")))]

@@

p_phases <- distribution_plot(df = scores[model != "Baseline"]) + 
  facet_wrap( ~ target_phase)

p_phases_wis <- distribution_plot_wis(df = scores) + 
  facet_wrap( ~ target_phase, scales = "free_x")

@@

pl_wis <- wrap_plots(p_combined_wis, p_wis, widths = c(1, 2)) / p_phases_wis + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

pl_wis
ggsave("plots/distribution_scores_wis.png")
